
---
title: "Reproducibility example: Birds"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(tidyverse)
```

## Introduction
Reading in the birds.csv data. This is morphological, ecological and geographical data for all birds taken from AVONET

```{r read_csv, eval=T}
birds <- read_csv("birds.csv")
```

## Plotting size relationships
This is a plot of the relationship between [tarsus length](https://en.wikipedia.org/wiki/Bird_measurement#Tarsus) and [wing length](https://en.wikipedia.org/wiki/Bird_measurement#Wing).

```{r graph}
ggplot(birds, aes(Tarsus.Length, Wing.Length)) + geom_point()
```

There are some outliers in this data. Some birds have very long tarsi and very short wings. This code identifies them by filtering birds that have tarsi length >200mm and wing length <300mm
```{r outliers}
birds %>%
  filter(Tarsus.Length > 200 & Wing.Length < 300) %>%
  pull(Species2_eBird) %>% unique()
```

## Write a function
This is a function to convert the measurements in the dataset from millimeters to centimeters
```{r function}
mm_to_cm <- function(x){
  return(x/10)
}
head(mm_to_cm(birds$Tarsus.Length), 10)
```

## Some bird queries

Which bird has the longest beak? Does it differ between culmen (from base of beak entering skull) or nares (from the nostril) measurements? The code below will return **only the top hits** from each measurement.

```{r longest_beak}
birds %>%
  arrange(desc(Beak.Length_Culmen))%>%
  head(10) %>%
  select(Species2_eBird, Beak.Length_Culmen)

birds %>%
  arrange(desc(Beak.Length_Nares))%>%
  head(10) %>%
  select(Species2_eBird, Beak.Length_Nares)
```

Pelecanus conspicillatus has the longest beak both measured by the culmen and the nares.


## Crows, ravens and magpies

Filter your dataset to include only common crows (*Corvus corone*), ravens (*Corvus corax*) and magpies (*Pica pica*). The code below is intended as a hint:

```{r code_block2, echo = TRUE}
birds_2 <- birds %>%
  filter(Species2_eBird == "Corvus corone" | Species2_eBird == "Corvus corax" | Species2_eBird == "Pica pica") 
```

Drawing a `ggplot2` boxplot of the beak length and depth distributions of these samples. 

```{r boxplot}
ggplot(birds_2, aes(Beak.Length_Culmen)) + geom_boxplot()
arrange(birds_2, desc(Beak.Length_Culmen))

ggplot(birds_2, aes(Beak.Depth)) + geom_boxplot()
arrange(birds_2, desc(Beak.Depth))
```
Corvus corax has the longest beak length and beak depth


